Paper_analyses

### 2021-11-15 Paper_Analyses_subj_obje_arousal.Rmd
initial commit on BADIA

@@

```{r}
library(readr)
clustering_agg_JASP <- read_csv("clustering_agg_JASP.csv")
View(clustering_agg_JASP)

@@

clustering3<- left_join(clustering2, cluster_stim)

@@

clustering_new$ssid<- as.factor(as.character(clustering_new$ssid))
clustering3

@@

>>>>

View(clustering)

@@

```{r}
library(readr)
View(clustering_agg_JASP)
clustering_agg_JASP <- read_csv("clustering_agg_JASP.csv")
View(clustering_agg_JASP)

@@

clustering3<- left_join(clustering2, cluster_stim)
nrow(clustering2)
nrow(clustering3)

@@

clustering_new$ssid<- as.factor(as.character(clustering_new$ssid))
View(clustering_new)

@@

clustering
clustering_agg
clustering_agg_JASP
clustering_agg2
clustering

clustering_new
# clustering3 has problems

# 1 dcast stim to columns

colnames(clustering_new)
colnames(clustering)

db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
                    ssid + TAS+AQ+Group ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))

library(data.table)
colnames(clustering_new)
library(tidyverse)

clustering_new_pre_PCA<- select(clustering_new, c(ssid, TAS, AQ, stimIAPS2, 
                                                  pup_basCor,Bio_Mean_HR_dif,
                                                  log_BIO_CDA.PhasicMax, arousal,
                                                  valence))
db_forPCA<- data.table::dcast(setDT(clustering_new_pre_PCA), 
                    ssid + TAS+AQ ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal', 'valence'))
